---
title: "Summary of data from rights-based approaches review"
output: html_notebook
---
This is a summary of results that I hope will be useful for writing and editing the article.  It can be automatically updated as we fix erros or tweak analyses in the code.  

You can hide the code itself using the box in the upper right hand corner, and see just the comments and outputs. 

```{r}
# this has to run to do the rest

# load required libaries

library(tidyverse)
library(RColorBrewer)
library(gridExtra)

# load data

fsv_data <- read_csv("input_data/fsv_data.csv")
r2f_data <- read_csv("input_data/r2f_data.csv")

fsv_data <- filter(fsv_data, graded == TRUE & excluded == FALSE)
r2f_data <- filter(r2f_data, graded == TRUE & excluded == FALSE)

# set factor levels where needed

fsv_data <- fsv_data %>% 
  mutate(impact_fsn = as.factor(impact_fsn)) %>%
  mutate(impact_fsn = fct_relevel(impact_fsn, c("-", "0", "+", "reverse+"))) %>%
  mutate(causality = as.factor(causality)) %>%
  mutate(causality = fct_relevel(causality, c("Descriptive", "Causal Effect", "Causal Mechanism"))) %>%
  mutate(conditionality = as.factor(conditionality)) %>%
  mutate(conditionality = fct_relevel(conditionality, c("Narrow", "Middle-range", "Universal"))) 


```

# Summary of results

This notebook provides an updatable (if we fix any issues in the keyed data or data cleaning code) summary of the data for the paper.

Here is a summary of the impacts (number of studies reporting -, 0, +, or reverse+)
```{r}
fsv_data %>%
  group_by(impact_fsn) %>%
  summarise(n())

r2f_data %>%
  group_by(impact_fsn) %>%
  summarise(n())
```

And here are the impacts grouped by "action type" (aka generalization logic)
```{r}
fsv_data %>% 
  group_by(gen_id, impact_fsn) %>% 
  summarise(n())


fsv_data %>% 
  group_by(gen_id, impact_fsn) %>% 
  summarise(n())
```

